Ecological management of stochastic systems with long transients

### 2020-07-09 manuscript/manuscript.Rmd
resubmit

fixed_sims <- 
 bind_rows("simulations under ghost policy function" = sim_ghost, 
           "simulations under bistable policy function" = sim_bistable, 
           .id = "prior") %>% 
  mutate(state = states[state], 
         action = actions[action])

@@

costs %>%
  ggplot(aes(time, cost, ymin = 0, ymax = cost, fill=model)) +
  geom_ribbon(alpha = 0.5) +
  ylab("Cost (net present value)") + xlab("time")
```

@@

sims_by_prior <- 
 bind_rows(fifty_fifty = sim_fiftyfifty, 
           seventy_thirty = sim_seventythirty, 
           .id = "prior")  %>% 
  mutate(state = states[state], 
         action = actions[action])

>>>>

fixed_sims <- 
 bind_rows("sims under ghost policy" = sim_ghost, 
           "sims under bistable policy" = sim_bistable, 
           .id = "prior") %>% 
  mutate(state = states[state], 
         action = actions[action])

@@

costs %>%
  ggplot(aes(time, cost, ymin = 0, ymax = cost, fill=model)) +
  geom_ribbon(alpha = 0.5) +
  ylab("Cost (net present value)") +
  xlab("time") +
  theme(legend.position="bottom")
```

@@

sims_by_prior <- 
 bind_rows("50-50 model prior" = sim_fiftyfifty, 
           "70-30 model prior" = sim_seventythirty, 
           .id = "prior")  %>% 
  mutate(state = states[state], 
         action = actions[action])
